A``Periodic Table'' for Bravais Lattices

### 2024-11-25 DeloneGrid/DeloneGrid.tex
Updating DeloneGrid paper. Herbert's revisions and a few of mine.

	\citeasnoun{Delaunay1932} and \citeasnoun{Delone1975} published a table of the Bravais types
	as distinguished by Selling (Delaunay) reduction.\cite{andrews2023measuring} published
	a somewhat modified version of Delaunay's table. The table presented here in Fig. \ref{grid}
	is arranged with the lattice family types as columns and the Federov polyhedron
	types \cite{fedorov1891symmetry} \cite{fedorov1885elements} as rows.
		\begin{figure}
		\includegraphics[width=15cm]{HorizontalDeloneGrid.eps}
		\label{grid}
		\caption{The  Bravais lattice types.}
	    \end{figure}

@@

	The columns are labeled according to the lattice family: cubic,
	tetragonal, rhombohedral, orthorhombic, monoclinic, and
	triclinic (anorthic). The labels for each reflect the names:
	\textbf{C}, \textbf{T}, \textbf{R}, \textbf{O},\textbf{ M}, \textbf{A}, \textbf{H} (rather than the choices of Delaunay: 
        \textbf{K}, \textbf{Q},	\textbf{R},\textbf{ O},\textbf{ M}, \textbf{T}, \textbf{H}, respectively).

	A further change from the model of Delaunay is the splitting 
	of orthorhombic and monoclinic into a pair of columns each
	($\bf{O_A}$, $\bf{O_B}$, $\bf{M_A}$, $\bf{M_B}$). This change 
	improved the display of these types. Delaunay had merged these
	disparate types into a single cell when their Federov
	types were identical. Thus, column $\bf{O}$ of \citeasnoun{Delaunay1932}
	has become columns $\bf{O_A}$ and $\bf{O_B}$, etc.

@@

	Except for rows 3 and 4, each row has a unique number of zero
	parameters. For rows 3 and 4, the difference is whether the two
	zeros are on opposite sides of the tetrahedron or on 
	adjacent sides.

@@

	The cells shown in gray have no corresponding Bravais type. For 
        instance, the cell that would be
	$\bf{H1}$ would be a hexagonal cell with no zero parameters
	(\it{i.e.} no 90$^{\circ}$ angles); 
	clearly an impossible case.

@@

>>>>

	\citeasnoun{Delaunay1932} and \citeasnoun{Delone1975} published a table of the Bravais types
	as distinguished by Selling (Delaunay) reduction.\cite{andrews2023measuring} published
	a somewhat modified version of Delaunay's table. The table presented here in Fig. \ref{grid}
	is arranged with the lattice family types as columns and the Federov polyhedron
	types \cite{fedorov1891symmetry} \cite{fedorov1885elements} as rows.
		\begin{figure}
		\includegraphics[width=15cm]{DeloneGridClaude_2-2.eps}
		\label{grid}
		\caption{The  Bravais lattice types.}
	    \end{figure}

@@

	The columns are labeled according to the lattice family: cubic,
	tetragonal, hexagonal-rhombohedral, orthorhombic, monoclinic, and
	triclinic (anorthic). The labels for each reflect the names:
	\textbf{C}, \textbf{T}, \textbf{H-R}, \textbf{O},\textbf{ M}, \textbf{A}, \textbf{H} (rather than the choices of Delaunay: 
        \textbf{K}, \textbf{Q},	\textbf{R},\textbf{ O},\textbf{ M}, \textbf{T}, \textbf{H}, respectively).

	In addition to combining the hexagonal and rhombohedral columns,
	a further change from the model of Delaunay is the splitting 
	of orthorhombic and monoclinic into a pair of columns each
	($\bf{O_A}$, $\bf{O_B}$, $\bf{M_A}$, $\bf{M_B}$). This change 
	improved the display of these types. Delaunay had merged these
	disparate types into a single cell when their Federov
	types were identical. Thus, column $\bf{O}$ of \citeasnoun{Delaunay1932}
	has become columns $\bf{O_A}$ and $\bf{O_B}$, etc.

@@

	Except for rows 3 and 4, each row has a unique number of zero
	parameters. For rows 3 and 4, the difference is whether the two
	zeros are on opposite sides of the tetrahedron (type 3) or on 
	adjacent sides (type 4). Type 3 is the case when the d-vector has
	a 90$^{\circ}$ angle to a, b, or c. Type 4 is the case
	where both 90$^{\circ}$ angles are among $\alpha$, $\beta$,
	and $\gamma$.

@@

	The cells shown in gray have no corresponding Bravais type.

@@

	$\bf{M3}$ is a 2-D manifold that is the boundary between
	 $\bf{M1A}$ and $\bf{M1B}$.
	With a characteristic of (rs0 ts0), $\bf{M3}$ has only three
	free parameters, not the four that are normal for an 
	monoclinic unit cell.

	There is a lack of unanimity in the crystallographic community
	on how best to present cells of the hexagonal-rhombohedral table cell
	in R1.  In the table we follow the convention of \cite{Burzlaff1985}
	of using the hR (rrr sss) \SVI{} lattice character (three equal
	cell edges and three equal cell angles $ \neq 90^{\circ}$).  It is equally valid to
	choose settings to combine the R1 cells in threes to form true 
	hexagonal H4 hP (00r rrs) super-cells with $a$ and $b$ as two equal edges
	with $\gamma=120^{\circ}$ and $\alpha = \beta = 90^{\circ}$, and the original
	hidden pair of lattice points along body diagonals of the supercells.
